---
title: "Slide template"
author: "Author Name"
institute: "Where Author Works"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 14pt
output:
  beamer_presentation:
    fig_height: 5
    fig_width: 8
    highlight: tango
    theme: metropolis
header-includes:
  - \usepackage{UMassRed_R}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, cache=TRUE, dev.args=list(bg=grey(0.9), pointsize=11))
```

# Basic Stuff

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

Use `\alert` to \alert{highlight} some text

## Slide with Enumerate

1. Item 1
2. Item 2
3. Item 3

###A title block
Just an example

# More stuff

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```


## Slide with mathematics

  Quantile Score for observation $y$.   For $0<p<1$:

  \begin{block}{}
    \[
      S(y_t,q_t(p)) = \left\{
      \begin{array}{rl}
      p(y_t-q_t(p)) & \text{if $y_t \ge q_t(p)$}\\
      (1-p)(q_t(p)-y_t) & \text{if $y_t < q_t(p)$}
      \end{array}\right.
    \]
  \end{block}
 
 Average score over all percentiles gives the best distribution forecast:
    \[
    QS = \frac{1}{99T}\sum_{p=1}^{99}\sum_{t=1}^T S(q_t(p),y_t)
    \]
 
